Quality Definitions of Qualities

### 2019-12-04 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Incorporation of comments on some of the definitions

The pattern in the presentation for each of the qualities is the same.  First we
summarize all of the definitions that we could find in the literature.  To keep
the clutter of quotation marks down, we have adopted the convention that each
definition is given verbatim from the cited source, but without showing
quotation marks.  After the summary of the existing definitions, we propose the
definition that we would like to work with going forward.  This definition can
either be our preference from the existing definitions, or a new definition,
which is often found by combining existing definitions.  Following the proposed
definition is an explanation for the reasoning that led to this choice.

@@

\begin{defn}
  A measure of the ease of installation \citep{smith2015comparing}.\wss{Where
    does this definition come from? Please add a citation.  Is it from
    \citet{McCallEtAl1977}? I thought so originally, but after looking into it,
    I don't think so anymore.}  \oo{@smith you added the definition in here but
    I guess it's from here} \wss{@olu, I was hoping you would verify the source
    of the definition.  Can you please find a pdf of the McCall reference and
    add it to our pub repo.  We should cite the primary source,
    but we can't assume what it says.}
\end{defn}

\begin{defn}
  The capability of a software product to be installed in a specified
  environment \citep{ISO9126}. (As summarized in
  \citep{berander2005software}.)  \wss{remove the quotation marks - we are
    assuming all definitions are directly quoted from the source. Please remove
    quotes for all of the definitions that you ``own.''}  \oo{Done} \wss{I've
    verified that this definition is correct.  We do not have to cite the
    textbook anymore, since we have the original source.}
\end{defn}

@@

Combined definitions \ref{Installability_Selected1} and
\ref{Installability_Selected2} rephrased.
Installability refers to the cost or effort required for the installation,
uninstallation or reinstallation of a software or product in a specified
enviroment.  \wss{This definition does not allow for
	measuring the machine time.}

@@

\begin{defn}  
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.  \wss{This is not how
    \citet{GhezziEtAl2003} defines correctness.  They only require satisfaction
    of the functional requirements.} \oo{Updated}

@@

\begin{defn}
  According to \citet{wilson2009quality}, the degree to which a system is free
  from defects in its specification, design, and implementation, is its
  correctness.
\end{defn}

@@

Definition~\ref{Correctness_Selected}: The degree to which a system or component
is free from faults in its specification, design and implementation.

@@

To determine whether a program is correct, we must be able to refer to both its
its specification, design and implementation to understand the intended purpose
and based on defined metrics, determine the extent to which this is met. Most
definitions of correctness refers only to functional specifications but this
definition is broad and is able to capture both functional and non-functional
specification without explicitly specifying it.\oo{We could modify te definition
  to explicitly state functional and non-functional if we decide.}  There is no
direct tool or method for measuring correctness. One way of building confidence
in correctness is by reviewing to ensure that each requirement stated is one
that the stakeholders and experts desire.  By maintaining traceability,
consistency and unambiguity, we can reduce the occurrence of errors and make the
goal of reviewing for correctness easier.

@@

@@

\begin{defn}
  A software is verifiable if its properties can be verified easily
  \citep{GhezziEtAl2003}.
\end{defn}

@@

\wss{In case we need it, here is a definition of testability.}

@@

\begin{defn}
  Validatability means solving the right equations \citep[p.~23]{Roache1998}.
  \oo{Validation?}
\end{defn}

\begin{defn} \label{Validatability_Selected} 
  Validation is the process of evaluating software during or at the end of the
  development process to determine whether it satisfies specified business
  requirements \citep{softwaretestingfundamentals}.
\end{defn}

\begin{defn}
  Validation refers to a different set of tasks that ensure that the software
  that has been built is traceable to customer requirements.
\end{defn}
\noindent \textbf{Proposed Definition}

@@

\begin{defn}
  Software validation checks that the software product satisfies or fits the
  intended use (high-level checking), i.e., the software meets the user
  requirements, not as specification artifacts or as needs of those who will
  operate the software only; but, as the needs of all the stakeholders (such as
  users, operators, administrators, managers, investors, etc.)
  \citep{WikipediaVnV}
\end{defn}

@@

\begin{defn}
  The probability that the software will operate as expected over a specified
  time interval \citep{GhezziEtAl2003}.
\end{defn}

@@

@@

Definition \ref{VisibilitySelected} points out that documentation is the way to
improve visibility. It is rephrased because the original one might refer to
binary status - ``visible'' or ``unvisible''.

>>>>

The pattern in the presentation for each of the qualities is the same.  First we
summarize all of the definitions that we could find in the literature.  To keep
the clutter of quotation marks down, we have adopted the convention that each
definition is given verbatim from the cited source, but without showing
quotation marks.  In cases where the definition has to be rephrased, quotation
marks are used to show those portions that are taken verbatim for the original
source.  After the summary of the existing definitions, we propose the
definition that we would like to work with going forward.  This definition can
either be our preference from the existing definitions, or a new definition,
which is often found by combining existing definitions.  Following the proposed
definition is an explanation for the reasoning that led to this choice.

In determining our recommended definition for each quality, we used the
following criteria:

\begin{description}
\item[Consistency] The final list of definitions should be consistent in the
  terminology used.  For instance, we do not use synonyms for variety; we use
  the same word to mean the same concept throughout the final list of
  definitions.  This is why measurement is given by ``the effort required..''
  and not the various synonyms for this that are seen in the literature. \wss{We
    may change this phrase we use for measuring something.  I just wanted to put
    this in here as a placeholder.}
\item[Generality]
\item[Measurability]
\item[Etc.]
\end{description}

@@

\begin{defn}
  A measure of the ease of installation \citep{smith2015comparing}.\wss{Where
    does this definition come from? Please add a citation.  Is it from
    \citet{McCallEtAl1977}? I thought so originally, but after looking into it,
    I don't think so anymore.}  \oo{@smith you added the definition in here but
    I guess it's from here} \wss{@olu, I was hoping you would verify the source
    of the definition.  Can you please find a pdf of the McCall reference and
    add it to our pub repo.  We should cite the primary source, but we can't
    assume what it says.  The source is definitely NOT
    \citep{smith2015comparing}.  By the way, you should use the BibTeX entries
    from References.bib in the pub repo when they are available.  This will save
    you time and make the citations more accurate. }  \wss{Olu, once we have the
    McCall reference, please verify all of the definitions where it is used, and
    remove the reference to the Van Vliet textbook.}
\end{defn}

\begin{defn}
  The capability of a software product to be installed in a specified
  environment \citep{ISO9126}. (As summarized in
  \citep{berander2005software}.)  \wss{remove the quotation marks - we are
    assuming all definitions are directly quoted from the source. Please remove
    quotes for all of the definitions that you ``own.''}  \oo{Done} \wss{I've
    verified that this definition is correct.  We do not have to cite the
    textbook anymore, since we have the original source.  Olu, please remove the
    \citep{berander2005software} in all instances where we have verified with
    the original source.}
\end{defn}

@@

Combined definitions \ref{Installability_Selected2} and
\ref{Installability_Selected1} rephrased.  Installability refers to the cost or
effort required for the installation, uninstallation or reinstallation of a
software or product in a specified environment.  \wss{This definition does not
  allow for measuring the machine time.  Do we want to distinguish between the
  human effort required and the total time of installation?  I think the human
  effort is the important metric here.}

@@

\begin{defn}  
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.  \wss{This is not how
    \citet{GhezziEtAl2003} defines correctness.  They only require satisfaction
    of the functional requirements.} \oo{Updated} \wss{Is this verbatim from the
    original source?  If not, we should show those parts that are verbatim in
    quotes, so that readers know the parts that were developed by us.}

@@

\begin{defn}
  According to \citet{wilson2009quality}, the degree to which a system is free
  from defects in its specification, design, and implementation, is its
  correctness.  \wss{Olu, can you please rephrase this one to match how the
    other definitions are presented.  That is, give the verbatim definition
    followed by the citation.}
\end{defn}

@@

Definition~\ref{Correctness_Selected}: The degree to which a system or component
is free from faults in its specification, design and implementation.  \wss{I
  think I prefer the Ghezzi definition, but with respect to all requirements
  (not just functional).}

@@

To determine whether a program is correct, we must be able to refer to both its
specification, design and implementation to understand the intended purpose and
based on defined metrics, determine the extent to which this is met. Most
definitions of correctness refers only to functional specifications but this
definition is broad and is able to capture both functional and non-functional
specification without explicitly specifying it.\oo{We could modify the
  definition to explicitly state functional and non-functional if we decide.}
There is no direct tool or method for measuring correctness. One way of building
confidence in correctness is by reviewing to ensure that each requirement stated
is one that the stakeholders and experts desire.  By maintaining traceability,
consistency and unambiguity, we can reduce the occurrence of errors and make the
goal of reviewing for correctness easier.

@@

\wss{We probably do not need the extra bits about measuring correctness and the
  dependency between correctness and other qualities.  We can discuss how to
  measure correctness as the next exercise we are doing after concluding the
  definitions exercise.  If the tradeoffs between qualities are important, we
  should cover that in a more systematic way.}

@@

\begin{defn}
  A software is verifiable if its properties can be verified easily
  \citep{GhezziEtAl2003}.  \wss{Is this a direct quote?}
\end{defn}

@@

@@

\begin{defn}
  Validatability means solving the right equations \citep[p.~23]{Roache1998}.
  \oo{Validation?}  \wss{We should also have the definition for verification
    about solving the equations right.}
\end{defn}

\begin{defn} \label{Validatability_Selected} 
  Validation is the process of evaluating software during or at the end of the
  development process to determine whether it satisfies specified business
  requirements \citep{softwaretestingfundamentals}.  \wss{Please use the
    author's name for this citation.  If that isn't known, use the name of the
    organization that published this material.}
\end{defn}

\begin{defn}
  Validation refers to a different set of tasks that ensure that the software
  that has been built is traceable to customer requirements.
\end{defn}

@@

\begin{defn}
  Software validation checks that the software product satisfies or fits the
  intended use (high-level checking), i.e., the software meets the user
  requirements, not as specification artifacts or as needs of those who will
  operate the software only; but, as the needs of all the stakeholders (such as
  users, operators, administrators, managers, investors, etc.)
  \citep{WikipediaVnV} \wss{This reference is not appearing in the Reference
    list.  We also don't really want a Wikipedia citation in a scholarly paper.
    Can you please find the source where this definition originally came from?}
\end{defn}

@@

\begin{defn}
  The probability that the software will operate as expected over a specified
  time interval \citep{GhezziEtAl2003}.  \wss{Is this verbatim from
    \citet{GhezziEtAl2003}?}
\end{defn}

@@

\wss{Olu, have you looked at the later chapters of the \citet{GhezziEtAl2003}?
  I believe there is a statistical definition of reliability there.}

@@

Definition \ref{VisibilitySelected} points out that documentation is the way to
improve visibility. It is rephrased because the original one might refer to
binary status - ``visible'' or ``invisible''.
